---
title: "9041 Assignment 2"
author: Selena Esteves
date: today
format: 
    html:
      toc: true
      code-fold: true
      code-summary: "Show code"
      df-print: paged
execute:
    echo: false
    warning: false
---

```{r, loading packages}
#| include: false

library(tidyverse)
library(psych)
library(gt)
library(janitor)
library(dplyr)
library(gtsummary)
library(quarto)
library(readxl)

Attachment_Anxiety_Data <- read_excel("Attachment_Anxiety_Data.xlsx")

print(exists("Attachment_Anxiety_Data"))

exists("Attachment_Anxiety_Data")

```
```{r, cleaning and mutating attachment and anxiety data}
#| include: false

attachment_anxiety <- Attachment_Anxiety_Data |>
  rename(
    gender = Gender,
    age_range = `Age group`,
    relationship_status = Relationship,
    ethnicity = Ethnicity
  ) |>
  mutate(
    gender = case_when(
      gender == 1 ~ "Male",
      gender == 2 ~ "Female",
      TRUE ~ NA_character_
    ),
    age_range = case_when(
      age_range == 1 ~ "18-24",
      age_range == 2 ~ "25-34",
      age_range == 3 ~ "35-44",
      age_range == 4 ~ "45-54",
      age_range == 5 ~ "55-64",
      TRUE ~ NA_character_
    )
  ) |>
  mutate(
    across(SA_1:SEst_10, as.integer)
  )
```
```{r, creating an answer key and scoring items}
#| include: false

SA_answer_key <- list(comp = c("SA_1","SA_2","SA_3","SA_4","-SA_5", "SA_6","SA_7","SA_8","-SA_9","SA_10","-SA_11","SA_12","SA_13","SA_14","SA_15","SA_16","SA_17","SA_18","SA_19","SA_20"))
AA_answer_key <- list(comp = c("AA_1","AA_2","AA_3","AA_4","AA_5","AA_6","AA_7","AA_8","AA_9"))
SEst_answer_key <- list(comp = c("SEst_1","-SEst_2","SEst_3","SEst_4","-SEst_5","-SEst_6","SEst_7","-SEst_8","-SEst_9","SEst_10"))

SA_scores <- scoreItems(SA_answer_key, attachment_anxiety, totals = F, min = 0, max = 4)
AA_scores <- scoreItems(AA_answer_key, attachment_anxiety, totals = F, min = 1, max = 7)
SEst_scores <- scoreItems(SEst_answer_key, attachment_anxiety, totals = F, min = 1, max = 4)

SA_scores$alpha
AA_scores$alpha
SEst_scores$alpha
```
```{r, making scores into data frames and combining all scores}
#| include: false

SA_scores.df <- as.data.frame(SA_scores$scores)
AA_scores.df <- as.data.frame(AA_scores$scores)
SEst_scores.df <- as.data.frame(SEst_scores$scores)

SA_AA_SEst_scores.df <- cbind(SA_scores.df, AA_scores.df, SEst_scores.df)

attachment_anxiety_outcomes <- cbind(
  gender = attachment_anxiety$gender,
  age_range = attachment_anxiety$age_range,
  SA_AA_SEst_scores.df
)

names(attachment_anxiety_outcomes)[3:5] <- c(
  "social_interaction_anxiety",
  "experiences_in_close_relationships_anxiety",
  "self_esteem"
)
```
```{r, demographic and summary tables}
#| include: false

demographic.table <- attachment_anxiety_outcomes |>
  select(gender, age_range) |>
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    missing = "no"
  )

demographic.table |>
  modify_caption("Table 1. Demographic Characteristics") |>
  as_gt()

summary <- describe(
  attachment_anxiety_outcomes[, c(
    "social_interaction_anxiety",
    "experiences_in_close_relationships_anxiety",
    "self_esteem"
  )]
)

N <- nrow(attachment_anxiety_outcomes)

summary.table <- summary |>
  mutate(
    Scale = c("Social Interaction Anxiety",
              "Experiences in Close Relationships Anxiety",
              "Self-Esteem"
    )
  ) |>
  relocate(.before = 1)

alphas <- round(c(
  SA_scores$alpha,
  AA_scores$alpha,
  SEst_scores$alpha
), 2)

summary.score.table <- summary.table |>
  select(Scale, mean, median, sd, range)
  
summary.scores <- cbind(summary.score.table, alphas)

summary.scores |>
  gt() |>
  tab_header(
    title = "Table 2. Participant Attachment, Anxiety, & Self-Esteem Outcomes"
    ) 
```
```{r, filtered summary tables}
#| include: false

filtered.summary <- attachment_anxiety_outcomes |>
  filter(gender == "Female")

filtered.summary.table <- describe(
  filtered.summary[, c(
    "social_interaction_anxiety",
    "experiences_in_close_relationships_anxiety",
    "self_esteem"
  )]
)

N <- nrow(filtered.summary.table)

filtered.summary.table <- filtered.summary.table |>
  mutate(
    Scale = c("Social Interaction Anxiety",
              "Experiences in Close Relationships Anxiety",
              "Self-Esteem"
    )
  )

filtered.summary.score.table <- filtered.summary.table |>
  select(Scale, mean, median, sd, range)

filtered.summary.score.table |>
  gt() |>
  tab_header(
    title = "Table 3. Female Participant Attachment, Anxiety, & Self-Esteem Outcomes"
  ) 
```

## Introduction 

The present study sought to explore attachment and social anxiety.

## Methods 

Participants were recruited via the University of Edinburgh’s online learning portal and social media platforms, as well as through word-of-mouth. A flyer with a link to the study was shared on these platforms along with a standard message explaining the purpose of the study, the inclusion criteria (i.e., must be over the age of 18), and the contact details of one of the researchers. The participants followed a link to the questionnaire, which was created using the Online Surveys platform. Participants responded to 3 questionnaires to measure 1) Attachment-related anxiety, 2) Social anxiety and 3) Self-esteem. They were also asked to report their gender, age group, relationship status and ethnicity. 

## Participants 

This study involved `r N` participants. Demographic characteristics of the present sample are depicted in Table 1.

`r demographic.table |>
  modify_caption("Table 1. Demographic Characteristics") |>
  as_gt()`

## Measures 

The present study explored the outcomes of interest using the Social Interaction Anxiety Scale, a shortened version of the Attachment-Related Anxiety subscale of the Experiences in Close Relationships Scale, and Rosenberg Self-Esteem Scale. Chronbach's alpha were calculated for each scale, reporting good to excellent reliability `r alphas <- round(c(
                          SA_scores$alpha,
                          AA_scores$alpha,
                          SEst_scores$alpha
                          ), 2)`, respectively.

## Data Analysis Strategy

Following data collection, data was cleaned by converting survey responses to integers and coding all responses according to the procedures outlined by the scale developers. Items 5, 9, and 11 in the Social Interaction Anxiety Scale and items 2, 5, 6, 8, and 9 in the Rosenberg Self-Esteem Scale were reverse coded. Answer keys were then developed in order to determine participant average scores across all 3 outcome variables.

## Results

The mean Social Interaction Anxiety score was `r round(mean(attachment_anxiety_outcomes$social_interaction_anxiety, na.rm = TRUE), 2)`, the mean Experiences in Close Relationships Anxiety score was `r round(mean(attachment_anxiety_outcomes$experiences_in_close_relationships_anxiety, na.rm = TRUE), 2)`, and the mean Self-Esteem score was `r round(mean(attachment_anxiety_outcomes$self_esteem, na.rm = TRUE), 2)`.All findings are depicted in Table 2.

`r summary.scores |>
  gt() |>
  tab_header(
    title = "Table 2. Participant Attachment, Anxiety, & Self-Esteem Outcomes"
    )`
    
Among female participants, the mean Social Interaction Anxiety score was `r round(mean(filtered.summary$social_interaction_anxiety, na.rm = TRUE), 2)`, the mean Experiences in Close Relationships Anxiety score was `r round(mean(filtered.summary$experiences_in_close_relationships_anxiety, na.rm = TRUE), 2)`, and the mean Self-Esteem score was `r round(mean(filtered.summary$self_esteem, na.rm = TRUE), 2)`. Findings among female participants are further depicted in Table 3.

```{r}
#| label: table-3
#| echo: false

filtered.summary <- attachment_anxiety_outcomes |>
  filter(gender == "Female")

filtered.summary.table <- describe(
  filtered.summary[, c(
    "social_interaction_anxiety",
    "experiences_in_close_relationships_anxiety",
    "self_esteem"
  )]
)

N <- nrow(filtered.summary.table)

filtered.summary.table <- filtered.summary.table |>
  mutate(
    Scale = c("Social Interaction Anxiety",
              "Experiences in Close Relationships Anxiety",
              "Self-Esteem"
    )
  )

filtered.summary.score.table <- filtered.summary.table |>
  select(Scale, mean, median, sd, range)

filtered.summary.score.table |>
  gt() |>
  tab_header(
    title = "Table 3. Female Participant Attachment, Anxiety, & Self-Esteem Outcomes"
  ) 
```
  